### `lfa_check_flag`

Check if a flag is set, indicating the completion of a specific process.


#### arguments

Argument      |Description
------------- |----------------
`flag_name`     |     A character string specifying the name of the flag file. It should be a descriptive and unique identifier for the process being checked.


#### description

This function checks for the existence of a hidden flag file at a specified location within the working directory. If the flag file is found, a message is printed, and the function returns `TRUE` to indicate that the associated processing step has already been completed. If the flag file is not found, the function returns `FALSE` , indicating that further processing can proceed.


#### value

A logical value indicating whether the flag is set ( `TRUE` ) or not ( `FALSE` ).


#### examples

```{r}
#| eval: false
# Check if the flag for a process named "data_processing" is set
lfa_check_flag("data_processing")
```


#### usage

```{r}
#| eval: false
lfa_check_flag(flag_name)
```


#### alias

lfa_check_flag


#### filename

lfa_check_flag.qmd


#### directory

/home/jakob/gi-master/project-courses/lidar-forest-analysis/src/results/appendix/package-docs



### `lfa_create_tile_location_objects`

Create tile location objects


#### author

Jakob Danel


#### description

This function traverses a directory structure to find LAZ files and creates
 tile location objects for each file. The function looks into the the `data` 
 directory of the repository/working directory. It then creates `tile_location` 
 objects based on the folder structure. The folder structure should not be
 touched by hand, but created by `lfa_init_data_structure()` which builds the
 structure based on a shape file.


#### seealso

[`tile_location`](#tilelocation)


#### value

A vector containing tile location objects.


#### examples

```{r}
#| eval: false
lfa_create_tile_location_objects()

lfa_create_tile_location_objects()
```


#### usage

```{r}
#| eval: false
lfa_create_tile_location_objects()
```


#### alias

lfa_create_tile_location_objects


#### filename

lfa_create_tile_location_objects.qmd


#### directory

/home/jakob/gi-master/project-courses/lidar-forest-analysis/src/results/appendix/package-docs



### `lfa_detection`

Perform tree detection on a lidar catalog and optionally save the results to a file.


#### arguments

Argument      |Description
------------- |----------------
`catalog`     |     A lidar catalog containing point cloud data. If set to NULL, the function attempts to read the catalog from the specified tile location.
`tile_location`     |     An object specifying the location of the lidar tile. If catalog is NULL, the function attempts to read the catalog from this tile location.
`write_to_file`     |     A logical value indicating whether to save the detected tree information to a file. Default is TRUE.


#### description

This function utilizes lidar data to detect trees within a specified catalog. The detected tree information can be optionally saved to a file in the GeoPackage format. The function uses parallel processing to enhance efficiency.


#### value

A sf style data frame containing information about the detected trees.


#### examples

```{r}
#| eval: false
# Perform tree detection on a catalog and save the results to a file
lfa_detection(catalog = my_catalog, tile_location = my_tile_location, write_to_file = TRUE)
```


#### usage

```{r}
#| eval: false
lfa_detection(catalog, tile_location, write_to_file = TRUE)
```


#### alias

lfa_detection


#### filename

lfa_detection.qmd


#### directory

/home/jakob/gi-master/project-courses/lidar-forest-analysis/src/results/appendix/package-docs



### `lfa_download_areas`

Download areas based on spatial features


#### arguments

Argument      |Description
------------- |----------------
`sf_areas`     |     Spatial features representing areas to be downloaded. It must include columns like "species" "name" See details for more information.


#### author

Jakob Danel


#### description

This function initiates the data structure and downloads areas based on spatial features.


#### details

The input data frame, `sf_areas` , must have the following columns:
  

*  "species": The species associated with the area. 

*  "name": The name of the area. 
 
 The function uses the `lfa_init_data_structure` function to set up the data structure
 and then iterates through the rows of `sf_areas` to download each specified area.


#### value

None


#### examples

```{r}
#| eval: false
lfa_download_areas(sf_areas)


# Example spatial features data frame
sf_areas <- data.frame(
species = c("SpeciesA", "SpeciesB"),
name = c("Area1", "Area2"),
# Must include also other attributes specialized to sf objects
# such as geometry, for processing of the download
)

lfa_download_areas(sf_areas)
```


#### usage

```{r}
#| eval: false
lfa_download_areas(sf_areas)
```


#### alias

lfa_download_areas


#### filename

lfa_download_areas.qmd


#### directory

/home/jakob/gi-master/project-courses/lidar-forest-analysis/src/results/appendix/package-docs



### `lfa_download`

Download an las file from the state NRW from a specific location


#### arguments

Argument      |Description
------------- |----------------
`species`     |     The species of the tree which is observed at this location
`name`     |     The name of the area that is observed
`location`     |     An sf object, which holds the location information for the area where the tile should be downloaded from.


#### description

It will download the file and save it to data/ list(list("html"), list(list("<species>"))) / list(list("html"), list(list("<name>"))) with the name of the tile


#### value

The LASCatalog object of the downloaded file


#### usage

```{r}
#| eval: false
lfa_download(species, name, location)
```


#### alias

lfa_download


#### filename

lfa_download.qmd


#### directory

/home/jakob/gi-master/project-courses/lidar-forest-analysis/src/results/appendix/package-docs



### `lfa_get_flag_path`

Get the path to a flag file indicating the completion of a specific process.


#### arguments

Argument      |Description
------------- |----------------
`flag_name`     |     A character string specifying the name of the flag file. It should be a descriptive and unique identifier for the process being flagged.


#### description

This function constructs and returns the path to a hidden flag file, which serves as an indicator that a particular processing step has been completed. The flag file is created in a designated location within the working directory.


#### value

A character string representing the absolute path to the hidden flag file.


#### examples

```{r}
#| eval: false
# Get the flag path for a process named "data_processing"
lfa_get_flag_path("data_processing")
```


#### usage

```{r}
#| eval: false
lfa_get_flag_path(flag_name)
```


#### alias

lfa_get_flag_path


#### filename

lfa_get_flag_path.qmd


#### directory

/home/jakob/gi-master/project-courses/lidar-forest-analysis/src/results/appendix/package-docs



### `lfa_ground_correction`

Correct the point clouds for correct ground imagery


#### arguments

Argument      |Description
------------- |----------------
`ctg`     |     An LASCatalog object. If not null, it will perform the actions on this object, if NULL inferring the catalog from the tile_location
`tile_location`     |     A tile_location type object holding the information about the location of the cataog. This is used to save the catalog after processing too.


#### author

Jakob Danel


#### description

This function is needed to correct the Z value of the point cloud, relative to the real
 ground height. After using this function to your catalog, the Z values can be seen as the
 real elevation about the ground. At the moment the function uses the `tin()` function from
 the `lidr` package. NOTE : The operation is inplace and can not be reverted, the old values
 of the point cloud will be deleted!


#### value

A catalog with the corrected z values. The catalog is always stored at tile_location and
 holding only the transformed values.


#### usage

```{r}
#| eval: false
lfa_ground_correction(ctg, tile_location)
```


#### alias

lfa_ground_correction


#### filename

lfa_ground_correction.qmd


#### directory

/home/jakob/gi-master/project-courses/lidar-forest-analysis/src/results/appendix/package-docs



### `lfa_init_data_structure`

Initialize data structure for species and areas


#### arguments

Argument      |Description
------------- |----------------
`sf_species`     |     A data frame with information about species and associated areas.


#### description

This function initializes the data structure for storing species and associated areas.


#### details

The input data frame, `sf_species` , should have at least the following columns:
  

*  "species": The names of the species for which the data structure needs to be initialized. 

*  "name": The names of the associated areas. 
 
 The function creates directories based on the species and area information provided in
 the `sf_species` data frame. It checks whether the directories already exist and creates
 them if they don't.


#### value

None


#### examples

```{r}
#| eval: false
# Example species data frame
sf_species <- data.frame(
species = c("SpeciesA", "SpeciesB"),
name = c("Area1", "Area2"),
# Other necessary columns
)

lfa_init_data_structure(sf_species)

# Example species data frame
sf_species <- data.frame(
species = c("SpeciesA", "SpeciesB"),
name = c("Area1", "Area2"),
# Other necessary columns
)

lfa_init_data_structure(sf_species)
```


#### usage

```{r}
#| eval: false
lfa_init_data_structure(sf_species)
```


#### alias

lfa_init_data_structure


#### filename

lfa_init_data_structure.qmd


#### directory

/home/jakob/gi-master/project-courses/lidar-forest-analysis/src/results/appendix/package-docs



### `lfa_init`

Initialize LFA (LiDAR forest analysis) data processing


#### arguments

Argument      |Description
------------- |----------------
`sf_file`     |     A character string specifying the path to the shapefile containing spatial features of research areas.


#### description

This function initializes the LFA data processing by reading a shapefile containing
 spatial features of research areas, downloading the specified areas, and creating
 tile location objects for each area.


#### details

This function reads a shapefile ( `sf_file` ) using the `sf` package, which should
 contain information about research areas. It then calls the `lfa_download_areas` 
 function to download the specified areas and `lfa_create_tile_location_objects` 
 to create tile location objects based on Lidar data files in those areas. The
 shapefile MUST follow the following requirements:
  

*  Each geometry must be a single object of type polygon 

*  Each entry must have the following attributes:  

*  species: A string describing the tree species of the area. 

*  name: A string describing the location of the area.


#### value

A vector containing tile location objects.


#### examples

```{r}
#| eval: false
# Initialize LFA processing with the default shapefile
lfa_init()

# Initialize LFA processing with a custom shapefile
lfa_init("custom_areas.shp")

# Example usage with the default shapefile
lfa_init()

# Example usage with a custom shapefile
lfa_init("custom_areas.shp")
```


#### usage

```{r}
#| eval: false
lfa_init(sf_file = "research_areas.shp")
```


#### alias

lfa_init


#### filename

lfa_init.qmd


#### directory

/home/jakob/gi-master/project-courses/lidar-forest-analysis/src/results/appendix/package-docs



### `lfa_intersect_areas`

Intersect Lidar Catalog with Spatial Features


#### arguments

Argument      |Description
------------- |----------------
`ctg`     |     A LAScatalog object representing the Lidar data to be processed.
`tile_location`     |     A tile location object representing the specific area of interest.
`areas_sf`     |     Spatial features defining areas.


#### description

This function intersects a Lidar catalog with a specific area defined by spatial features.


#### details

The function intersects the Lidar catalog specified by `ctg` with a specific area defined by
 the `tile_location` object and `areas_sf` . It removes points outside the specified area and
 returns a modified LAScatalog object.
 
 The specified area is identified based on the `species` and `name` attributes in the
 `tile_location` object. If a matching area is not found in `areas_sf` , the function
 stops with an error.
 
 The function then transforms the spatial reference of the identified area to match that of
 the Lidar catalog using `sf::st_transform` .
 
 The processing is applied to each chunk in the catalog using the `identify_area` function,
 which merges spatial information and filters out points that are not classified as inside
 the identified area. After processing, the function writes the modified LAS files back to
 the original file locations, removing points outside the specified area.
 
 If an error occurs during the processing of a chunk, a warning is issued, and the function
 continues processing the next chunks. If no points are found after filtering, a warning is
 issued, and NULL is returned.


#### seealso

Other functions in the Lidar forest analysis (LFA) package.


#### value

A modified LAScatalog object with points outside the specified area removed.


#### examples

```{r}
#| eval: false
# Example usage
lfa_intersect_areas(ctg, tile_location, areas_sf)

# Example usage
lfa_intersect_areas(ctg, tile_location, areas_sf)
```


#### usage

```{r}
#| eval: false
lfa_intersect_areas(ctg, tile_location, areas_sf)
```


#### alias

lfa_intersect_areas


#### filename

lfa_intersect_areas.qmd


#### directory

/home/jakob/gi-master/project-courses/lidar-forest-analysis/src/results/appendix/package-docs



### `lfa_load_ctg_if_not_present`

Loading the catalog if it is not present


#### arguments

Argument      |Description
------------- |----------------
`ctg`     |     Catalog object. Can be NULL
`tile_location`     |     The location to look for the catalog tiles, if their are not present


#### description

This function checks if the catalog is `NULL` . If it is it will load the
 catalog from the `tile_location`


#### value

The provided ctg object if not null, else the catalog for the tiles
 of the tile_location.


#### usage

```{r}
#| eval: false
lfa_load_ctg_if_not_present(ctg, tile_location)
```


#### alias

lfa_load_ctg_if_not_present


#### filename

lfa_load_ctg_if_not_present.qmd


#### directory

/home/jakob/gi-master/project-courses/lidar-forest-analysis/src/results/appendix/package-docs



### `lfa_map_tile_locations`

Map Function Over Tile Locations


#### arguments

Argument      |Description
------------- |----------------
`tile_locations`     |     A list of tile location objects.
`map_function`     |     The mapping function to be applied to each tile location.
`...`     |     Additional arguments to be passed to the mapping function.


#### description

This function applies a specified mapping function to each tile location in a list.


#### details

This function iterates over each tile location in the provided list ( `tile_locations` )
 and applies the specified mapping function ( `map_function` ) to each tile location.
 The mapping function should accept a tile location object as its first argument, and
 additional arguments can be passed using the ellipsis ( `...` ) syntax.
 
 This function is useful for performing operations on multiple tile locations concurrently,
 such as loading Lidar data, processing areas, or other tasks that involve tile locations.


#### seealso

The mapping function provided should be compatible with the structure and requirements
 of the tile locations and the specific task being performed.


#### value

None


#### examples

```{r}
#| eval: false
# Example usage
lfa_map_tile_locations(tile_locations, my_mapping_function, param1 = "value")

# Example usage
lfa_map_tile_locations(tile_locations, my_mapping_function, param1 = "value")
```


#### usage

```{r}
#| eval: false
lfa_map_tile_locations(tile_locations, map_function, check_flag = NULL, ...)
```


#### alias

lfa_map_tile_locations


#### filename

lfa_map_tile_locations.qmd


#### directory

/home/jakob/gi-master/project-courses/lidar-forest-analysis/src/results/appendix/package-docs



### `lfa_merge_and_save`

Merge and Save Text Files in a Directory


#### arguments

Argument      |Description
------------- |----------------
`input_directory`     |     The path to the input directory containing text files.
`output_name`     |     The name for the output file where the merged content will be saved.


#### description

This function takes an input directory and an output name as arguments.
 It merges the textual content of all files in the specified directory into
 a single string, with each file's content separated by a newline character.
 The merged content is then saved into a file named after the output name
 in the same directory. After the merging is complete, all input files are
 deleted.


#### details

This function reads the content of each text file in the specified input directory
 and concatenates them into a single string. Each file's content is separated by a newline
 character. The merged content is then saved into a file named after the output name
 in the same directory. Finally, all input files are deleted from the directory.


#### seealso

[`readLines`](#readlines) , [`writeLines`](#writelines) , [`file.remove`](#file.remove)


#### value

This function does not explicitly return any value. It prints a message
 indicating the successful completion of the merging and saving process.


#### examples

```{r}
#| eval: false
# Merge text files in the "data_files" directory and save the result in "merged_output"
lfa_merge_and_save("data_files", "merged_output")

# Merge text files in the "data_files" directory and save the result in "merged_output"
lfa_merge_and_save("data_files", "merged_output")
```


#### usage

```{r}
#| eval: false
lfa_merge_and_save(input_directory, output_name)
```


#### alias

lfa_merge_and_save


#### filename

lfa_merge_and_save.qmd


#### directory

/home/jakob/gi-master/project-courses/lidar-forest-analysis/src/results/appendix/package-docs



### `lfa_rd_to_qmd`

Convert Rd File to Markdown


#### arguments

Argument      |Description
------------- |----------------
`rdfile`     |     The path to the Rd file or a parsed Rd object.
`outfile`     |     The path to the output Markdown file (including the file extension).
`append`     |     Logical, indicating whether to append to an existing file (default is FALSE).


#### description

IMPORTANT NOTE: 
 This function is nearly identical to the `Rd2md::Rd2markdown` function from the `Rd2md` 
 package. We needed to implement our own version of it because of various reasons:
  

*  The algorithm uses hardcoded header sizes (h1 and h2 in original) which is not feasible for our use-case of the markdown. 

*  We needed to add some Quarto Markdown specifics, e.g. to make sure that the examples will not be runned. 

*  We want to exclude certain tags from our implementation.


#### details

For that reason we copied the method and made changes as needed and also added this custom documentation.
 
 This function converts an Rd (R documentation) file to Markdown format (.md) and
 saves the converted file at the specified location. The function allows appending
 to an existing file or creating a new one. The resulting Markdown file includes
 sections for the function's name, title, and additional content such as examples,
 usage, arguments, and other sections present in the Rd file.
 
 The function performs the following steps:
  

*  Parses the Rd file using the Rd2md package. 

*  Creates a Markdown file with sections for the function's name, title, and additional content. 

*  Appends the content to an existing file if `append` is set to TRUE. 

*  Saves the resulting Markdown file at the specified location.


#### seealso

[`Rd2md::parseRd`](#rd2md::parserd)


#### value

This function does not explicitly return any value. It saves the converted Markdown file
 at the specified location as described in the details section.


#### examples

```{r}
#| eval: false
# Convert Rd file to Markdown and save it
lfa_rd_to_md("path/to/your/file.Rd", "path/to/your/output/file.md")

# Convert Rd file to Markdown and append to an existing file
lfa_rd_to_md("path/to/your/file.Rd", "path/to/existing/output/file.md", append = TRUE)
```


#### usage

```{r}
#| eval: false
lfa_rd_to_qmd(rdfile, outfile, append = FALSE)
```


#### alias

lfa_rd_to_qmd


#### filename

lfa_rd_to_qmd.qmd


#### directory

/home/jakob/gi-master/project-courses/lidar-forest-analysis/src/results/appendix/package-docs



### `lfa_rd_to_results`

Convert Rd Files to Markdown and Merge Results


#### description

This function converts all Rd (R documentation) files in the "man" directory
 to Markdown format (.qmd) and saves the converted files in the "results/appendix/package-docs" directory.
 It then merges the converted Markdown files into a single string and saves
 the merged content into a file named "docs.qmd" in the "results/appendix/package-docs" directory.


#### details

The function performs the following steps:
  

*  Removes any existing "docs.qmd" file in the "results/appendix/package-docs" directory. 

*  Finds all Rd files in the "man" directory. 

*  Converts each Rd file to Markdown format (.qmd) using the `lfa_rd_to_qmd` function. 

*  Saves the converted Markdown files in the "results/appendix/package-docs" directory. 

*  Merges the content of all converted Markdown files into a single string. 

*  Saves the merged content into a file named "docs.qmd" in the "results/appendix/package-docs" directory.


#### seealso

[`lfa_rd_to_qmd`](#lfardtoqmd) , [`lfa_merge_and_save`](#lfamergeandsave)


#### value

This function does not explicitly return any value. It performs the conversion,
 merging, and saving operations as described in the details section.


#### examples

```{r}
#| eval: false
# Convert Rd files to Markdown and merge the results
lfa_rd_to_results()
```


#### usage

```{r}
#| eval: false
lfa_rd_to_results()
```


#### alias

lfa_rd_to_results


#### filename

lfa_rd_to_results.qmd


#### directory

/home/jakob/gi-master/project-courses/lidar-forest-analysis/src/results/appendix/package-docs



### `lfa_segmentation`

Segment the elements of an point cloud by trees


#### arguments

Argument      |Description
------------- |----------------
`ctg`     |     An LASCatalog object. If not null, it will perform the actions on this object, if NULL inferring the catalog from the tile_location
`tile_location`     |     A tile_location type object holding the information about the location of the catalog. This is used to save the catalog after processing too.


#### author

Jakob Danel


#### description

This function will try to to divide the hole point cloud into unique trees.
 Therefore it is assigning for each chunk of the catalog  a `treeID` for each
 point. Therefore the algorithm uses the `li2012` implementation with the
 following parameters: `li2012(dt1 = 2, dt2 = 3, R = 2, Zu = 10, hmin = 5, speed_up = 12)` 
 NOTE : The operation is in place and can not be reverted, the old values
 of the point cloud will be deleted!


#### value

A catalog where each chunk has additional `treeID` values indicating the belonging tree.


#### usage

```{r}
#| eval: false
lfa_segmentation(ctg, tile_location)
```


#### alias

lfa_segmentation


#### filename

lfa_segmentation.qmd


#### directory

/home/jakob/gi-master/project-courses/lidar-forest-analysis/src/results/appendix/package-docs



### `lfa_set_flag`

Set a flag to indicate the completion of a specific process.


#### arguments

Argument      |Description
------------- |----------------
`flag_name`     |     A character string specifying the name of the flag file. It should be a descriptive and unique identifier for the process being flagged.


#### description

This function creates a hidden flag file at a specified location within the working directory to indicate that a particular processing step has been completed. If the flag file already exists, a warning is issued.


#### value

This function does not have a formal return value.


#### examples

```{r}
#| eval: false
# Set the flag for a process named "data_processing"
lfa_set_flag("data_processing")
```


#### usage

```{r}
#| eval: false
lfa_set_flag(flag_name)
```


#### alias

lfa_set_flag


#### filename

lfa_set_flag.qmd


#### directory

/home/jakob/gi-master/project-courses/lidar-forest-analysis/src/results/appendix/package-docs


