# Installation and Intro

This chapter is used to introduce in how to install this package and how to get
started.

## Installation
The easiest way to install the package is by using:
```{r}
devtools::install_github("https://github.com/jakobdanel/lidar-forest-analysis")
```
This controls that you always use the latest version of this package. Other
installation options, e.g. building from source, are described inside the repos
[README](https://github.com/jakobdanel/lidar-forest-analysis).

After you have done that we can start exploring the package
```{r}
library(lfa)
```


## Getting started
First of all we need to download the data and initialize a structure in which we
are able to do all the processing and analysis we want to do with our data. Therefore
a shapefile containing all the data is used. This repository uses a file called
`research_areas.shp`, but you can use each shapefile you want. Important for these
shapefiles is, that the file is containing a simple set of polygons, for each of these
polygons two attributes need to be set:

1. `species` - the name of the species which is dominant for the area
2. `name` - the name of the area from where the data should be collected as an
identifier

*NOTE:* Each pair of `species`and `name` must be unique in the dataset.

You also need to specify were to run all of this code, because it will use
the relative location to the working directory for storing data. In detail the package
will create a directory `data` as a sub directory of the working-directory and storing
all the data inside of this directory. In this tutorial we will use as wori+king directory
the repository directory.
With this shapefile we can init our project:
```{r}
setwd("..")
tile_locations <- lfa_init(sf_file = "research_areas.shp")
```
The function returning a list of something called tile_location, a type which is
used in this project to specify the location of LAS files. We can look into the first entry of the list
to see what happens
```{r}
tile_locations[[1]]
```

Each tile_location object storing information on `species` and `name` as their are
specified with the polygons. Also their are storing information for the `tile_location`,
this is the name of the LAS file after the naming convention of the state NRW. 
If one polygon is inside areas of multipe of these files, we can identify the data
with this attributes.
With the help of this objects we can use many of the functions for preprocessing and
analysis.